---
title: "Double Cylinder_Markdown"
author: "Christoph Voelter"
date: "December 11, 2018"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)


library(lme4)
library(readr)
library(tidyverse)
library(sjPlot)
library(ggthemes)
library(gridExtra)
library(reshape2)
#library(Hmisc)
library("PerformanceAnalytics")
source("C:/Users/cjv3/R/R scripts/Roger/diagnostic_fcns.r")
source("C:/Users/cjv3/R/R scripts/Roger/glmm_stability.r")
source("C:/Users/cjv3/R/R scripts/Roger/boxplotteR.r")
source("C:/Users/cjv3/R/R scripts/Roger/boot_glmm.r")
source("C:/Users/cjv3/R/R scripts/Roger/corr_exact.r")
#load(file ="mm1_mult_poss.RData")
#readRDS(file ="multpos_model.rds")
```




```{r loading data, include = FALSE}
#Preparing code for mixed modeling. 
Double.cyl.data <- read.table(file="data/20181211Doublecylinder_data_sweetwaters.txt", header=T, sep="\t") #%>%

  #  filter(Subject != "Julia" & Subject != "Mwanzo" & Subject != "Safari") #did not complete test trials


```

```{r eval=FALSE, include=FALSE}
summary(Double.cyl.data )
```



#### Transparent vs opaque phase

```{r dc plot, echo=FALSE}
#correct
dc_individual <- Double.cyl.data %>%
  filter(!is.na(correct)) %>%
  group_by(Condition2, Subject) %>% 
  summarize(dc.correct = mean(correct)) %>% 
  add_count(dc.correct)

  
dc_individual$Condition2 <- factor(dc_individual$Condition2, levels = c("transparent", "opaque"))


p1<-  ggplot(
  data=dc_individual, aes(x=Condition2, y=dc.correct, group=Condition2)) +
  geom_boxplot()+
  geom_point(size = dc_individual$n, colour = "purple")+
  ylim(0,1)+
  #xlim(0,2)+
#  geom_line(lty=2)+
  labs(x="",y="Mean proportion of correct choices")+
  theme_few()+
  #theme(axis.text.x=element_blank(), axis.ticks.x=element_blank())+
  ggtitle("Choice performance")+
  geom_hline(yintercept=1/3, linetype="dashed", color = "red")


#peeking



dc_individual2 <- Double.cyl.data %>%
  filter(!is.na(peeking)) %>%
  group_by(Condition2, Subject) %>% 
  summarize(dc.peeking = mean(peeking)) %>% 
  add_count(dc.peeking)

  
dc_individual2$Condition2 <- factor(dc_individual$Condition2, levels = c("transparent", "opaque"))

p2<-  ggplot(
  data=dc_individual2, aes(x=Condition2, y=dc.peeking, group=Condition2)) +
  geom_boxplot()+
  geom_point(size = dc_individual2$n, colour = "purple")+
  ylim(0,1)+
  #xlim(0,2)+
#  geom_line(lty=2)+
  labs(x="",y="Mean proportion of peeking")+
  theme_few()+
  #theme(axis.text.x=element_blank(), axis.ticks.x=element_blank())+
  ggtitle("Peeking")

  grid.arrange(p1, p2, nrow=1)

```


####Choice performance: Comparison to chance

* DV: mean performance of correct choices.
* Chance value: 1/3

```{r echo=FALSE}
tt<-t.test( dc_individual[dc_individual$Condition2=="transparent",]$dc.correct, mu=1/3, alternative = "two.sided")
```
* Transparent condition (pretest): Mean = `r round(tt$estimate, 2)`, 95% CI [`r round(tt$conf.int[1],2)`, `r round(tt$conf.int[2],2)`], *t*(`r tt$parameter`)=`r round(tt$statistic,2)`, *p*=`r round(tt$p.value,5)` 

```{r echo=FALSE}
tt<-t.test( dc_individual[dc_individual$Condition2=="opaque",]$dc.correct, mu=1/3, alternative = "two.sided")
```
* Opaque condition (test): Mean = `r round(tt$estimate, 2)`, 95% CI [`r round(tt$conf.int[1],2)`, `r round(tt$conf.int[2],2)`], *t*(`r tt$parameter`)=`r round(tt$statistic,2)`, *p*=`r round(tt$p.value,3)`

***  

#### Opaque phase: peeking vs no peeking

```{r dc plot3, echo=FALSE}
#correct
dc_individual_peek <- Double.cyl.data %>%
  filter(!is.na(correct)) %>%
  filter(Condition2=="opaque") %>%
  group_by(peeking, Subject) %>% 
  summarize(dc.correct = mean(correct)) %>% 
  add_count(dc.correct) %>%
  ungroup() %>% 
  mutate(peeking=recode(peeking, `0`="No", `1`="Yes"))

  ggplot(
  data=dc_individual_peek, aes(x=peeking, y=dc.correct, group=peeking)) +
  geom_boxplot()+
  geom_point(size = dc_individual_peek$n, colour = "purple")+
  ylim(0,1)+
  #xlim(0,2)+
#  geom_line(lty=2)+
  labs(x="Peeking",y="Mean number of correct choices")+
  theme_few()+
  #theme(axis.text.x=element_blank(), axis.ticks.x=element_blank())+
  ggtitle("Choice performance")+
  geom_hline(yintercept=1/3, linetype="dashed", color = "red")



```




```{r  echo=FALSE}

##peeking overall
dc_individual3 <- Double.cyl.data %>%
  filter(!is.na(peeking)) %>%
  filter(Condition2=="opaque") %>%
  group_by(baiting, Subject) %>% 
  summarize(dc.peeking = mean(peeking)) %>% 
  add_count(dc.peeking)

  
#dc_individual2$Condition2 <- factor(dc_individual$Condition2, levels = c("transparent", "opaque"))

#p1<-  
ggplot(
  data=dc_individual3, aes(x=baiting, y=dc.peeking, group=baiting)) +
  geom_boxplot()+
  geom_point(size = dc_individual3$n, colour = "purple")+
  ylim(0,1)+
  #xlim(0,2)+
#  geom_line(lty=2)+
  labs(x="Visible baiting",y="Mean proportion of peeking")+
  theme_few()+
  #theme(axis.text.x=element_blank(), axis.ticks.x=element_blank())+
  ggtitle("Peeking - opaque condition")
```

```{r echo=FALSE}
dc_individual4 <- Double.cyl.data %>%
  filter(!is.na(peek_above)) %>%
  filter(Condition2=="opaque") %>%
  group_by(baiting, Subject) %>% 
  summarize(dc.peek_above = mean(peek_above)) %>% 
  add_count(dc.peek_above)

  
#dc_individual2$Condition2 <- factor(dc_individual$Condition2, levels = c("transparent", "opaque"))

#p2<-  
ggplot(
  data=dc_individual4, aes(x=baiting, y=dc.peek_above, group=baiting)) +
  geom_boxplot()+
  geom_point(size = dc_individual4$n, colour = "purple")+
  ylim(0,1)+
  #xlim(0,2)+
#  geom_line(lty=2)+
  labs(x="Visible baiting",y="Mean proportion of peeking above")+
  theme_few()+
  #theme(axis.text.x=element_blank(), axis.ticks.x=element_blank())+
  ggtitle("Peeking above - opaque condition")

```

```{r echo=FALSE}
##Peeking below
dc_individual5 <- Double.cyl.data %>%
  filter(!is.na(peek_below)) %>%
  filter(Condition2=="opaque") %>%
  group_by(baiting, Subject) %>% 
  summarize(dc.peek_below = mean(peek_below)) %>% 
  add_count(dc.peek_below)

  
#dc_individual2$Condition2 <- factor(dc_individual$Condition2, levels = c("transparent", "opaque"))

#p3<-  
ggplot(
  data=dc_individual5, aes(x=baiting, y=dc.peek_below, group=baiting)) +
  geom_boxplot()+
  geom_point(size = dc_individual5$n, colour = "purple")+
  ylim(0,1)+
  #xlim(0,2)+
#  geom_line(lty=2)+
  labs(x="Visible baiting",y="Mean proportion of peeking below")+
  theme_few()+
  #theme(axis.text.x=element_blank(), axis.ticks.x=element_blank())+
  ggtitle("Peeking below - opaque condition")


 #grid.arrange(p1, p2,p3)

```


```{r echo=FALSE}
knitr::knit_exit()
```


####GLMM 01

look ~ Test phase + Trial number within phase + Age + (1+Test phase + Trial number within phase | Subject), family = binomial.

+ Scale variables: trial number, age, and order of conditions
```{R include=FALSE}
Double.cyl.data$z.trial=as.vector(scale(Double.cyl.data$trial_number))
Double.cyl.data$z.age=as.vector(scale(Double.cyl.data$Age))
```


```{r}
#coding dummy variables before centering the slopes
Double.cyl.data$Condition.c<-as.numeric(Double.cyl.data$Condition2==levels(Double.cyl.data$Condition2)[2])
Double.cyl.data$Condition.c=Double.cyl.data$Condition.c-mean(Double.cyl.data$Condition.c)

```

### Run Model

####Full model
```{r}
contr=glmerControl(optimizer="bobyqa", optCtrl=list(maxfun=10000000))
glmm01=glmer(peeking ~ Condition2+z.trial+z.age+
               (1+z.trial+Condition2|Subject),
             data=Double.cyl.data, family=binomial, control=contr)
```


####Null model	 
```{r}	 
null01=glmer(peeking ~ 1+(1+z.trial+Condition2|Subject),
             data=Double.cyl.data, family=binomial, control=contr)
```
####Full-null model comparison
```{r echo=FALSE}	 
round(anova(null01, glmm01, test="Chisq"),3)
```

```{r}
xdrop1=drop1(glmm01, test="Chisq",control=contr)
round(xdrop1,3)
```




####GLMM 02a
GLMM2a: To analyse the effects of condition (within the test phase only) on participants looking above the occluder / double-cylinders:
Presence of above looks ~ Condition + Trial number within test phase + Age + (1+Condition + Trial number within test phase | Subject), family =binomial

```{r}

Double.cyl.data.opaque<-Double.cyl.data%>%
  filter(Condition2=="opaque")
```


+ Scale variables: trial number, age, and order of conditions
```{R include=FALSE}
Double.cyl.data.opaque$z.trial=as.vector(scale(Double.cyl.data.opaque$trial_number))
Double.cyl.data.opaque$z.age=as.vector(scale(Double.cyl.data.opaque$Age))
```


```{r}
#coding dummy variables before centering the slopes
Double.cyl.data.opaque$Condition.c<-as.numeric(Double.cyl.data.opaque$Condition2==levels(Double.cyl.data.opaque$Condition2)[2])
Double.cyl.data.opaque$Condition.c=Double.cyl.data.opaque$Condition.c-mean(Double.cyl.data.opaque$Condition.c)

```

### Run Model

####Full model
```{r}
contr=glmerControl(optimizer="bobyqa", optCtrl=list(maxfun=10000000))
glmm02a=glmer(peek_above ~ baiting+z.trial+z.age+
              (1|Subject)+(0+z.trial+baiting|Subject),
             data=Double.cyl.data.opaque, family=binomial, control=contr)
```


####Null model	 
```{r}	 
null02a=glmer(peek_above ~ 1+
               (1|Subject)+(0+z.trial+baiting|Subject),
             data=Double.cyl.data.opaque, family=binomial, control=contr)
```
####Full-null model comparison
```{r echo=FALSE}	 
round(anova(null02a, glmm02a, test="Chisq"),3)
```

```{r}
xdrop2a=drop1(glmm02a, test="Chisq",control=contr)
round(xdrop2c,3)
```





####GLMM 02c
GLMM2c: To analyse the effects of condition (within the test phase only) on participants looking both above and below the occluder / double-cylinders:
Presence of both an above and a below look ~ Condition + Trial number within test phase  + Age + (1+Condition + Trial number within test phase | Subject), family =binomial

```{r}

Double.cyl.data.opaque<-Double.cyl.data%>%
  filter(Condition2=="opaque")
```


+ Scale variables: trial number, age, and order of conditions
```{R include=FALSE}
Double.cyl.data.opaque$z.trial=as.vector(scale(Double.cyl.data.opaque$trial_number))
Double.cyl.data.opaque$z.age=as.vector(scale(Double.cyl.data.opaque$Age))
```


```{r}
#coding dummy variables before centering the slopes
Double.cyl.data.opaque$Condition.c<-as.numeric(Double.cyl.data.opaque$Condition2==levels(Double.cyl.data.opaque$Condition2)[2])
Double.cyl.data.opaque$Condition.c=Double.cyl.data.opaque$Condition.c-mean(Double.cyl.data.opaque$Condition.c)

```

### Run Model

####Full model
```{r}
contr=glmerControl(optimizer="bobyqa", optCtrl=list(maxfun=10000000))
glmm02c=glmer(peeking ~ baiting+z.trial+z.age+
              (1|Subject)+(0+z.trial+baiting|Subject),
             data=Double.cyl.data.opaque, family=binomial, control=contr)
```


####Null model	 
```{r}	 
null02c=glmer(peeking ~ 1+
               (1|Subject)+(0+z.trial+baiting|Subject),
             data=Double.cyl.data.opaque, family=binomial, control=contr)
```
####Full-null model comparison
```{r echo=FALSE}	 
round(anova(null02c, glmm02c, test="Chisq"),3)
```

```{r}
xdrop2c=drop1(glmm02c, test="Chisq",control=contr)
round(xdrop2c,3)
```




```{r echo=FALSE}
knitr::knit_exit()
```


















####Proportions of correct choices
 

####Comparison to chance

* DV: mean performance of correct choices (until criterion or until the maximum number of trials was reached)  
* Chance value: 0.5 

```{r echo=FALSE}
tt<-t.test(Shifting.boxes_individual$Shifting.boxes.correct[Shifting.boxes_individual$Condition=="SD"] , mu=0.25, alternative = "two.sided")

```
* **SD**: Mean correct vs chance value (0.5): Mean = `r round(tt$estimate, 2)`, 95% CI [`r round(tt$conf.int[1],2)`, `r round(tt$conf.int[2],2)`], *t*(`r tt$parameter`)=`r round(tt$statistic,2)`, *p*=`r round(tt$p.value,3)` 

```{r echo=FALSE}
tt<-t.test(Shifting.boxes_individual$Shifting.boxes.correct[Shifting.boxes_individual$Condition=="SR"] , mu=0.5, alternative = "two.sided")

```
* **SR**: Mean correct vs chance value (0.5): Mean = `r round(tt$estimate, 2)`, 95% CI [`r round(tt$conf.int[1],2)`, `r round(tt$conf.int[2],2)`], *t*(`r tt$parameter`)=`r round(tt$statistic,2)`, *p*=`r round(tt$p.value,3)` 

```{r echo=FALSE}
tt<-t.test(Shifting.boxes_individual$Shifting.boxes.correct[Shifting.boxes_individual$Condition=="CD"] , mu=0.5, alternative = "two.sided")

```
* **CD**: Mean correct vs chance value (0.5): Mean = `r round(tt$estimate, 2)`, 95% CI [`r round(tt$conf.int[1],2)`, `r round(tt$conf.int[2],2)`], *t*(`r tt$parameter`)=`r round(tt$statistic,2)`, *p*=`r round(tt$p.value,3)` 

```{r echo=FALSE}
tt<-t.test(Shifting.boxes_individual$Shifting.boxes.correct[Shifting.boxes_individual$Condition=="ID"] , mu=0.5, alternative = "two.sided")

```
* **ID**: Mean correct vs chance value (0.5): Mean = `r round(tt$estimate, 2)`, 95% CI [`r round(tt$conf.int[1],2)`, `r round(tt$conf.int[2],2)`], *t*(`r tt$parameter`)=`r round(tt$statistic,2)`, *p*=`r round(tt$p.value,3)` 

```{r echo=FALSE}
tt<-t.test(Shifting.boxes_individual$Shifting.boxes.correct[Shifting.boxes_individual$Condition=="ED"] , mu=0.5, alternative = "two.sided")

```
* **ED** (Box discrimination with different filling materials): Mean correct vs chance value (0.5): Mean = `r round(tt$estimate, 2)`, 95% CI [`r round(tt$conf.int[1],2)`, `r round(tt$conf.int[2],2)`], *t*(`r tt$parameter`)=`r round(tt$statistic,2)`, *p*=`r round(tt$p.value,3)` 

```{r echo=FALSE}
Shifting.boxes_individualED <- Shifting.boxes.data %>%
  filter(!is.na(correct)) %>%
  filter(Condition == "ED")%>%
  group_by(SessionED, Subject) %>% 
  summarize(Shifting.boxes.correct = mean(correct)) %>% 
  add_count(Shifting.boxes.correct)
```
```{r echo=FALSE}
tt<-t.test(Shifting.boxes_individualED$Shifting.boxes.correct[Shifting.boxes_individualED$SessionED==1] , mu=0.5, alternative = "two.sided")

```


* **ED Session 1**: Mean correct vs chance value (0.5): Mean = `r round(tt$estimate, 2)`, 95% CI [`r round(tt$conf.int[1],2)`, `r round(tt$conf.int[2],2)`], *t*(`r tt$parameter`)=`r round(tt$statistic,2)`, *p*=`r round(tt$p.value,3)` 

```{r echo=FALSE}
tt<-t.test(Shifting.boxes_individualED$Shifting.boxes.correct[Shifting.boxes_individualED$SessionED==2] , mu=0.5, alternative = "two.sided")

```


* **ED Session 2**: Mean correct vs chance value (0.5): Mean = `r round(tt$estimate, 2)`, 95% CI [`r round(tt$conf.int[1],2)`, `r round(tt$conf.int[2],2)`], *t*(`r tt$parameter`)=`r round(tt$statistic,2)`, *p*=`r round(tt$p.value,3)` 


```{r echo=FALSE}
tt<-t.test(Shifting.boxes_individual$Shifting.boxes.correct[Shifting.boxes_individual$Condition=="EDSD"] , mu=0.5, alternative = "two.sided")

```
* **EDSD** (Box discrimination with identical filling materials): Mean correct vs chance value (0.5): Mean = `r round(tt$estimate, 2)`, 95% CI [`r round(tt$conf.int[1],2)`, `r round(tt$conf.int[2],2)`], *t*(`r tt$parameter`)=`r round(tt$statistic,2)`, *p*=`r round(tt$p.value,3)` 


***


####Trial-to-trial effects
```{r echo=FALSE}

###Plotting material_changes
plot_shifting_boxes_material <- Shifting.boxes.data %>%
  filter(material_changes!="") %>%
  filter(Condition == "ED")%>%
  group_by(material_changes, Subject) %>% 
  summarize(correct_resp = mean(correct)) %>% 
  add_count(correct_resp)

plot_shifting_boxes_material_mean <- plot_shifting_boxes_material %>% 
  group_by(material_changes) %>% 
  summarize(mean_correct = mean(correct_resp)) 

p1 <- 
  ggplot(
  data=plot_shifting_boxes_material, aes(x=material_changes, y=correct_resp, group = material_changes)) +   
  geom_boxplot()+
  geom_point(size = plot_shifting_boxes_material$n, colour = "purple") +
  ylim(0,1)+
  labs(x="Material Change",y="Mean correct")+
  geom_hline(yintercept=0.5, linetype="dashed", color = "red")+
  theme_few()+
  #scale_y_Shifting Boxes - ED")+
  stat_compare_means(aes(group = material_changes), paired = TRUE, method="t.test", label.x = 1.3)#, label = "p.signif")




###Plotting side_changes

plot_shifting_boxes_side <- Shifting.boxes.data %>%
  filter(side_changes!="") %>%
  filter(Condition == "ED")%>%
  group_by(side_changes, Subject) %>% 
  summarize(correct_resp = mean(correct)) %>% 
  add_count(correct_resp)

plot_shifting_boxes_side_mean <- plot_shifting_boxes_side %>% 
  group_by(side_changes) %>% 
  summarize(mean_correct = mean(correct_resp)) 

p2 <- 
  ggplot(
  data=plot_shifting_boxes_side, aes(x=side_changes, y=correct_resp, group = side_changes)) +   
  geom_boxplot()+
  geom_point(size = plot_shifting_boxes_side$n, colour = "purple") +
  ylim(0,1)+
  labs(x="Side Change",y="Mean correct")+
  theme_few()+
  geom_hline(yintercept=0.5, linetype="dashed", color = "red")+
  #scale_y_Shifting Boxes - ED")+
  stat_compare_means(aes(group = side_changes), paired = TRUE, method="t.test", label.x = 1.3)#, label = "p.signif")

grid.arrange(p1, p2, nrow = 1, heights=unit(100, "mm"))
 
```


####Plotting box preferences  

```{r echo=FALSE, warning=FALSE}

plot_boxes_distractorS1 <- Shifting.boxes.data %>%
  filter(Condition == "ED")%>%
  filter(SessionED == 1)%>%
  group_by(chosen_distractor, Subject) %>% 
  count(chosen_distractor) %>%
  mutate(n = n/20)
  

p1<-
  ggplot(plot_boxes_distractorS1, aes(x=n, fill=chosen_distractor)) +
    geom_histogram(binwidth=0.05, alpha=.5, position="identity")+
    scale_color_brewer(palette="Dark2")+
    scale_fill_brewer(palette="Dark2")+
    ylim(0,6)+
    xlim(0,1)+
    labs(x="",y="Distractor choices")+
    theme_few()+
    #theme(axis.text.x=element_blank(), axis.ticks.x=element_blank())+
    theme(legend.position="none")+
    #scale_y_continuous(breaks=seq(0,1,0.25))+
    ggtitle("Session 1")

plot_boxes_distractorS2 <- Shifting.boxes.data %>%
  filter(Condition == "ED")%>%
  filter(SessionED == 2)%>%
  group_by(chosen_distractor, Subject) %>% 
  count(chosen_distractor) %>%
  mutate(n = n/20)

p2<-ggplot(plot_boxes_distractorS2, aes(x=n, fill=chosen_distractor)) +
    geom_histogram(binwidth=0.05, alpha=.5, position="identity")+
    scale_color_brewer(palette="Dark2")+
    scale_fill_brewer(palette="Dark2")+
    ylim(0,6)+
    xlim(0,1)+
    labs(x="",y="Distractor choices")+
    theme_few()+
    #theme(axis.text.x=element_blank(), axis.ticks.x=element_blank())+
    theme(legend.position="none")+
    #scale_y_continuous(breaks=seq(0,1,0.25))+
    ggtitle("Session 2")

grid.arrange(p1, p2, nrow = 1)
```

***   

### Task-switching  


```{r shifting shelf plot, echo=FALSE}

###shelf
Shifting.shelf_individual <- Shifting.shelf.data %>%
  filter(!is.na(correct)) %>%
  group_by(Condition, Subject) %>% 
  summarize(Shifting.shelf.correct = mean(correct)) %>% 
  add_count(Shifting.shelf.correct)

Shifting.shelf_mean <- Shifting.shelf_individual %>%
  group_by(Condition) %>% 
  summarize(mean_val=mean(Shifting.shelf.correct)) 


#c(rep(1, 29),rep(2,29))
#p1<-  
Shifting.shelf_individual$Condition <- factor(Shifting.shelf_individual$Condition, levels = c("Training01", "Training02", "Test"))
  ggplot(
  data=Shifting.shelf_individual, aes(x=Condition, y=Shifting.shelf.correct, group=Condition)) +
  geom_boxplot()+
  geom_point(size = Shifting.shelf_individual$n, colour = "purple")+
  ylim(0,1)+
  #xlim(0,2)+
#  geom_line(lty=2)+
  labs(x="",y="Mean number of correct choices")+
  theme_few()+
  #theme(axis.text.x=element_blank(), axis.ticks.x=element_blank())+
  ggtitle("Shifting shelf")+
  geom_hline(yintercept=0.5, linetype="dashed", color = "red")
```


####Comparison to chance

* DV: mean performance of correct choices (until criterion or until the maximum number of trials was reached)  
* Chance value: 0.5 

```{r echo=FALSE}
tt<-t.test(Shifting.shelf_individual$Shifting.shelf.correct[Shifting.shelf_individual$Condition=="Training01"] , mu=0.5, alternative = "two.sided")

```
* **First training phase**: Mean correct vs chance value (0.5): Mean = `r round(tt$estimate, 2)`, 95% CI [`r round(tt$conf.int[1],2)`, `r round(tt$conf.int[2],2)`], *t*(`r tt$parameter`)=`r round(tt$statistic,2)`, *p*=`r round(tt$p.value,3)` 

```{r echo=FALSE}
tt<-t.test(Shifting.shelf_individual$Shifting.shelf.correct[Shifting.shelf_individual$Condition=="Training02"] , mu=0.5, alternative = "two.sided")

```
* **Second training phase**: Mean correct vs chance value (0.5): Mean = `r round(tt$estimate, 2)`, 95% CI [`r round(tt$conf.int[1],2)`, `r round(tt$conf.int[2],2)`], *t*(`r tt$parameter`)=`r round(tt$statistic,2)`, *p*=`r round(tt$p.value,3)` 

```{r echo=FALSE}
tt<-t.test(Shifting.shelf_individual$Shifting.shelf.correct[Shifting.shelf_individual$Condition=="Test"] , mu=0.5, alternative = "two.sided")

```
* **Test phase**: Mean correct vs chance value (0.5): Mean = `r round(tt$estimate, 2)`, 95% CI [`r round(tt$conf.int[1],2)`, `r round(tt$conf.int[2],2)`], *t*(`r tt$parameter`)=`r round(tt$statistic,2)`, *p*=`r round(tt$p.value,3)` 

  
####Switching mistakes and number of switches between platforms

```{r echo=FALSE}

###Plotting switching mistakes
plot_shifting_shelf_sm <- Shifting.shelf.data %>%
  filter(!is.na(switching_mistakes)) %>%
  group_by(Subject) %>% 
  summarize(shelf_switching_mistakes = sum(switching_mistakes)) %>% 
  add_count(shelf_switching_mistakes)

#max(plot_shifting_shelf_sm$shelf_switching_mistakes)

p1 <- 
  ggplot(
  data=plot_shifting_shelf_sm , aes(x=c(rep(1, 25)), y=shelf_switching_mistakes)) +   geom_boxplot()+
  geom_point(size = plot_shifting_shelf_sm$n, colour = "purple") +
  ylim(0,20)+
  xlim(0,2)+
  labs(x="",y="Switching mistakes")+
  # geom_hline(yintercept=0.5, linetype="dashed", color = "red")+
  theme_few()+
  theme(axis.text.x=element_blank(), axis.ticks.x=element_blank())+
   ggtitle("Switching mistakes")


###Plotting switches between platforms
plot_shifting_shelf_switches <- Shifting.shelf.data %>%
  filter(!is.na(Switches)) %>%
  group_by(Subject) %>% 
  summarize(shelf_switches = sum(Switches)) %>% 
  add_count(shelf_switches)

#max(plot_shifting_shelf_switches$shelf_switches)

p2 <- 
  ggplot(
  data=plot_shifting_shelf_switches , aes(x=c(rep(1, 25)), y=shelf_switches)) +   geom_boxplot()+
  geom_point(size = plot_shifting_shelf_switches$n, colour = "purple") +
  ylim(0,10)+
  xlim(0,2)+
  labs(x="",y="Platform switches")+
  # geom_hline(yintercept=0.5, linetype="dashed", color = "red")+
  theme_few()+
  theme(axis.text.x=element_blank(), axis.ticks.x=element_blank())+
   ggtitle("Platform switches")

grid.arrange(p1, p2, nrow = 1, heights=unit(100, "mm"))
 
```



```{r aggregating data for correlation analysis, include=FALSE}
# Shifting tray
Shifting.tray_individual_session <- Shifting.tray.data %>%
  group_by(Session,  Subject) %>% 
  summarize(Shifting.tray.correct = mean(correct)) %>% 
  spread( Session, Shifting.tray.correct)%>%
  rename(Shifting.tray.correct.S1="1")%>%
  rename(Shifting.tray.correct.S2="2")

Shifting.tray_individual <- Shifting.tray.data %>%
  group_by(Subject) %>% 
  summarize(Shifting.tray.correct = mean(correct))

#Shifting boxes
Shifting.boxes_individual_wide <- Shifting.boxes_individual %>%
  select(-n) %>%
  spread( Condition, Shifting.boxes.correct)

#Task switching
Shifting.shelf_individual_test <- Shifting.shelf_individual %>%
  filter(Condition=="Test") %>%
  ungroup() %>% 
  select(-Condition, -n)

shifting_shelf_sm <- Shifting.shelf.data %>%
  filter(!is.na(switching_mistakes)) %>%
  group_by(Subject) %>% 
  summarize(shelf_switching_mistakes = sum(switching_mistakes))

shifting_shelf_switches <- Shifting.shelf.data %>%
  filter(!is.na(Switches)) %>%
  group_by(Subject) %>% 
  summarize(shelf_switches = sum(Switches))

#######################################################
#Join DVs together

Shifting_task_individual <- Shifting.tray_individual  %>% 
  full_join(Shifting.tray_individual_session  ) %>%
  full_join(Shifting.shelf_individual_test ) %>%
  full_join(shifting_shelf_sm ) %>%
  full_join(shifting_shelf_switches) %>%
  full_join(Shifting.boxes_individual_wide)
  

```


*** 

###Shifting tray task

####Trial-to-trial effects
```{r echo=FALSE}

###Plotting side_changes
plot_individual_side <- Shifting.tray.data %>%
  filter(Subject != "George")%>%
  group_by(Session, side_change, Subject) %>% 
  summarize(correct_resp = mean(correct)) 


plot_ind_S1_side <- plot_individual_side %>% 
  filter(Session == 1 & side_change!="")%>%
  add_count(correct_resp)

plot_ind_S1_side_mean <- plot_ind_S1_side %>% 
  group_by(side_change) %>% 
  summarize(mean_correct = mean(correct_resp)) 

p1 <- ggplot(
  data=plot_ind_S1_side, aes(side_change, correct_resp, group = Subject)) +   
  geom_point(size = plot_ind_S1_side$n, colour = "purple") +
  geom_line(lty=2)+
  ylim(0,1)+
  labs(x="Side Change",y="Mean correct")+
  theme_few()+
  #scale_y_continuous(breaks=seq(0,1,0.25))+
  ggtitle("Session 1")+
  geom_segment(aes(y = plot_ind_S1_side_mean$mean_correct[1], yend = plot_ind_S1_side_mean$mean_correct[1], x = 1 -0.2, xend = 1 + 0.2))+
  geom_segment(aes(y = plot_ind_S1_side_mean$mean_correct[2], yend = plot_ind_S1_side_mean$mean_correct[2], x = 2 -0.2, xend = 2 + 0.2))+
  stat_compare_means(aes(group = side_change), paired = TRUE, method="t.test", label.x = 1.3)#, label = "p.signif")
 


plot_ind_S2_side <- plot_individual_side %>% 
  filter(Session == 2 & side_change!="")%>%
  add_count(correct_resp)

plot_ind_S2_side_mean <- plot_ind_S2_side %>% 
  group_by(side_change) %>% 
  summarize(mean_correct = mean(correct_resp)) 

p2 <- ggplot(
  data=plot_ind_S2_side, aes(side_change, correct_resp, group = Subject)) +   
  geom_point(size = plot_ind_S2_side$n, colour = "purple") +
  geom_line(lty=2)+
  ylim(0,1)+
  labs(x="Side Change",y="Mean correct")+
  theme_few()+
 # scale_y_continuous(breaks=seq(0,1,0.25))+
  ggtitle("Session 2")+
  geom_segment(aes(y = plot_ind_S2_side_mean$mean_correct[1], yend = plot_ind_S2_side_mean$mean_correct[1], x = 1 -0.2, xend = 1 + 0.2))+
  geom_segment(aes(y = plot_ind_S2_side_mean$mean_correct[2], yend = plot_ind_S2_side_mean$mean_correct[2], x = 2 -0.2, xend = 2 + 0.2))+
  stat_compare_means(aes(group = side_change), paired = TRUE, method="t.test", label.x = 1.3)#, label = "p.signif")
 

###plotting box changes
plot_individual_box <- Shifting.tray.data %>%
  filter(Subject != "George")%>%
  group_by(Session, box_change, Subject) %>% 
  summarize(correct_resp = mean(correct)) 

plot_ind_S1_box <- plot_individual_box %>% 
  filter(Session == 1 & box_change!="")%>%
  add_count(correct_resp)

plot_ind_S1_box_mean <- plot_ind_S1_box %>% 
  group_by(box_change) %>% 
  summarize(mean_correct = mean(correct_resp)) 

p3 <- ggplot(
  data=plot_ind_S1_box , aes(box_change, correct_resp, group = Subject)) +   
  geom_point(size = plot_ind_S1_box $n, colour = "purple") +
  geom_line(lty=2)+
  ylim(0,1)+
  labs(x="Box Change",y="Mean correct")+
  theme_few()+
 # scale_y_continuous(breaks=seq(0,1,0.25))+
  geom_segment(aes(y = plot_ind_S1_box_mean $mean_correct[1], yend = plot_ind_S1_box_mean $mean_correct[1], x = 1 -0.2, xend = 1 + 0.2))+
  geom_segment(aes(y = plot_ind_S1_box_mean$mean_correct[2], yend = plot_ind_S1_box_mean $mean_correct[2], x = 2 -0.2, xend = 2 + 0.2))+
  stat_compare_means(aes(group = box_change), paired = TRUE, method="t.test", label.x = 1.3)#, label = "p.signif")
 




plot_ind_S2_box  <- plot_individual_box %>% 
  filter(Session == 2 & box_change!="")%>%
  add_count(correct_resp)

plot_ind_S2_box_mean <- plot_ind_S2_box %>% 
  group_by(box_change) %>% 
  summarize(mean_correct = mean(correct_resp)) 

p4 <- ggplot(
  data=plot_ind_S2_box , aes(box_change, correct_resp, group = Subject)) +   
  geom_point(size = plot_ind_S2_box $n, colour = "purple") +
  geom_line(lty=2)+
  ylim(0,1)+
  labs(x="Box Change",y="Mean correct")+
  theme_few()+
 # scale_y_continuous(breaks=seq(0,1,0.25))+
  geom_segment(aes(y = plot_ind_S2_box_mean $mean_correct[1], yend = plot_ind_S2_box_mean $mean_correct[1], x = 1 -0.2, xend = 1 + 0.2))+
  geom_segment(aes(y = plot_ind_S2_box_mean$mean_correct[2], yend = plot_ind_S2_box_mean $mean_correct[2], x = 2 -0.2, xend = 2 + 0.2))+
  stat_compare_means(aes(group = box_change), paired = TRUE, method="t.test", label.x = 1.3)#, label = "p.signif")
 

grid.arrange(p1, p2,p3,p4, nrow = 2)
 #g <- arrangeGrob(p1, p2,p3,p4, nrow = 2)
#ggsave("tray_shifting_trial effects.jpeg",g, width = 10, height = 7)



```


####T-tests

#####Side changes  

```{r echo=FALSE}
tt<-t.test( plot_ind_S1_side[plot_ind_S1_side$side_change=="no",]$correct_resp, plot_ind_S1_side[plot_ind_S1_side$side_change=="yes",]$correct_resp, paired = TRUE, alternative = "two.sided")
```
* Session 1: Mean difference = `r round(tt$estimate, 2)`, 95% CI [`r round(tt$conf.int[1],2)`, `r round(tt$conf.int[2],2)`], *t*(`r tt$parameter`)=`r round(tt$statistic,2)`, *p*=`r round(tt$p.value,3)` 


```{r echo=FALSE}
tt<-t.test( plot_ind_S2_side[plot_ind_S2_side$side_change=="no",]$correct_resp, plot_ind_S2_side[plot_ind_S2_side$side_change=="yes",]$correct_resp, paired = TRUE, alternative = "two.sided")
```
* Session 2: Mean difference = `r round(tt$estimate, 2)`, 95% CI [`r round(tt$conf.int[1],2)`, `r round(tt$conf.int[2],2)`], *t*(`r tt$parameter`)=`r round(tt$statistic,2)`, *p*=`r round(tt$p.value,3)` 

#####Box changes 
```{r echo=FALSE}
tt<-t.test( plot_ind_S1_box[plot_ind_S1_box$box_change=="no",]$correct_resp, plot_ind_S1_box[plot_ind_S1_box$box_change=="yes",]$correct_resp, paired = TRUE, alternative = "two.sided")
```
* Session 1: Mean difference = `r round(tt$estimate, 2)`, 95% CI [`r round(tt$conf.int[1],2)`, `r round(tt$conf.int[2],2)`], *t*(`r tt$parameter`)=`r round(tt$statistic,2)`, *p*=`r round(tt$p.value,3)` 

```{r echo=FALSE}
tt<-t.test( plot_ind_S2_box[plot_ind_S2_box$box_change=="no",]$correct_resp, plot_ind_S2_box[plot_ind_S2_box$box_change=="yes",]$correct_resp, paired = TRUE, alternative = "two.sided")
```
* Session 2: Mean difference = `r round(tt$estimate, 2)`, 95% CI [`r round(tt$conf.int[1],2)`, `r round(tt$conf.int[2],2)`], *t*(`r tt$parameter`)=`r round(tt$statistic,2)`, *p*=`r round(tt$p.value,3)` 

#####Comparison to chance
* Chance value: 0.5  

```{r echo=FALSE}
plot_individual <- Shifting.tray.data %>%
  group_by(Session, Subject) %>% 
  summarize(correct_resp = mean(correct)) 
tt<-t.test( plot_individual[plot_individual$Session==1,]$correct_resp, mu=0.5, alternative = "two.sided")
```
* Session 1: Mean = `r round(tt$estimate, 2)`, 95% CI [`r round(tt$conf.int[1],2)`, `r round(tt$conf.int[2],2)`], *t*(`r tt$parameter`)=`r round(tt$statistic,2)`, *p*=`r round(tt$p.value,3)` 

```{r echo=FALSE}
tt<-t.test( plot_individual[plot_individual$Session==2,]$correct_resp, mu=0.5, alternative = "two.sided")
```
* Session 2: Mean = `r round(tt$estimate, 2)`, 95% CI [`r round(tt$conf.int[1],2)`, `r round(tt$conf.int[2],2)`], *t*(`r tt$parameter`)=`r round(tt$statistic,2)`, *p*=`r round(tt$p.value,3)` 

####Plotting box preferences
```{r include=FALSE}



plot_individual_distractor1 <- Shifting.tray.data %>%
  filter(Subject != "George" & Subject != "Saidia" & Subject != "Safari" )%>%
  filter(Session == 1)%>%
  group_by(chosen_distractor, Subject) %>% 
  count(chosen_distractor) %>%
  mutate(n = n/24)
  

p1<-ggplot(plot_individual_distractor1, aes(x=n, fill=chosen_distractor)) +
    geom_histogram(binwidth=0.05, alpha=.5, position="identity")+
   ylim(0,8)+
   xlim(0,1)+
   labs(x="",y="Count of distractor choices per subject")+
   theme_few()+
   theme(axis.text.x=element_blank(), axis.ticks.x=element_blank(), legend.position="none")+
  #scale_y_continuous(breaks=seq(0,1,0.25))+
   ggtitle("Session 1")

plot_individual_distractor2 <- Shifting.tray.data %>%
  filter(Subject != "George" & Subject != "Saidia" & Subject != "Safari" )%>%
  filter(Session == 2)%>%
  group_by(chosen_distractor, Subject) %>% 
  count(chosen_distractor) %>%
  mutate(n = n/24)

p2<-ggplot(plot_individual_distractor2, aes(x=n, fill=chosen_distractor)) +
    geom_histogram(binwidth=0.05, alpha=.5, position="identity")+
   ylim(0,8)+
   xlim(0,1)+
   labs(x="",y="Count of distractor choices per subject")+
   theme_few()+
   theme(axis.text.x=element_blank(), axis.ticks.x=element_blank(), legend.position="none")+
  #scale_y_continuous(breaks=seq(0,1,0.25))+
   ggtitle("Session 2")


grid.arrange(p1, p2, nrow = 1)




```

```{r warning=FALSE, echo=FALSE}



plot_individual_distractor1 <- Shifting.tray.data %>%
  filter(Subject != "George" & Subject != "Saidia" & Subject != "Safari" )%>%
  filter(Session == 1)%>%
  filter(trial_number < 13)%>%
  group_by(chosen_distractor, Subject) %>% 
  count(chosen_distractor) %>%
  mutate(n = n/12)
  

p1<-ggplot(plot_individual_distractor1, aes(x=n, fill=chosen_distractor)) +
    geom_histogram(binwidth=0.05, alpha=.5, position="identity")+
scale_color_brewer(palette="Dark2")+
  scale_fill_brewer(palette="Dark2")+
   ylim(0,11)+
   xlim(0,1)+
   labs(x="",y="Distractor choices")+
   theme_few()+
   #theme(axis.text.x=element_blank(), axis.ticks.x=element_blank())+
  theme(legend.position="none")+
  #scale_y_continuous(breaks=seq(0,1,0.25))+
   ggtitle("Session 1 - first half")

plot_individual_distractor2 <- Shifting.tray.data %>%
  filter(Subject != "George" & Subject != "Saidia" & Subject != "Safari" )%>%
  filter(Session == 1)%>%
  filter(trial_number > 12)%>%
  group_by(chosen_distractor, Subject) %>% 
  count(chosen_distractor) %>%
  mutate(n = n/12)

p2<-ggplot(plot_individual_distractor2, aes(x=n, fill=chosen_distractor)) +
    geom_histogram(binwidth=0.05, alpha=.5, position="identity")+
  scale_color_brewer(palette="Dark2")+
  scale_fill_brewer(palette="Dark2")+
   ylim(0,11)+
   xlim(0,1)+
   labs(x="",y="Distractor choices")+
   theme_few()+
   #theme(axis.text.x=element_blank(), axis.ticks.x=element_blank())+
  theme(legend.position="none")+
  #scale_y_continuous(breaks=seq(0,1,0.25))+
   ggtitle("Session 1 - second half")

plot_individual_distractor3 <- Shifting.tray.data %>%
  filter(Subject != "George" & Subject != "Saidia" & Subject != "Safari" )%>%
  filter(Session == 2)%>%
  filter(trial_number < 13)%>%
  group_by(chosen_distractor, Subject) %>% 
  count(chosen_distractor) %>%
  mutate(n = n/12)
  

p3<-ggplot(plot_individual_distractor3, aes(x=n, fill=chosen_distractor)) +
    geom_histogram(binwidth=0.05, alpha=.5, position="identity")+
  scale_color_brewer(palette="Dark2")+
  scale_fill_brewer(palette="Dark2")+
   ylim(0,11)+
   xlim(0,1)+
   labs(x="",y="Distractor choices")+
   theme_few()+
   #theme(axis.text.x=element_blank(), axis.ticks.x=element_blank())+
  theme(legend.position="none")+
  #scale_y_continuous(breaks=seq(0,1,0.25))+
   ggtitle("Session 2 - first half")

plot_individual_distractor4 <- Shifting.tray.data %>%
  filter(Subject != "George" & Subject != "Saidia" & Subject != "Safari" )%>%
  filter(Session == 2)%>%
  filter(trial_number > 12)%>%
  group_by(chosen_distractor, Subject) %>% 
  count(chosen_distractor) %>%
  mutate(n = n/12)

p4<-ggplot(plot_individual_distractor4, aes(x=n, fill=chosen_distractor)) +
    geom_histogram(binwidth=0.05, alpha=.5, position="identity")+
    scale_color_brewer(palette="Dark2")+
    scale_fill_brewer(palette="Dark2")+
    ylim(0,11)+
    xlim(0,1)+
    labs(x="",y="Distractor choices")+
    theme_few()+
    #theme(axis.text.x=element_blank(), axis.ticks.x=element_blank())+
    theme(legend.position="none")+
    #scale_y_continuous(breaks=seq(0,1,0.25))+
   ggtitle("Session 2 - second half")
 


p5<-ggplot(plot_individual_distractor4, aes(x=n, fill=chosen_distractor)) +
    geom_histogram(binwidth=0.05, alpha=.5, position="identity")+
scale_color_brewer(palette="Dark2")+
  scale_fill_brewer(palette="Dark2")+
  theme(legend.position="top")

#grid.arrange(p1, p2,p3,p4, nrow = 2)


legend <- get_legend(p5)
# 3. Remove the legend from the box plot
grid.arrange(p1, p2,p3,p4,legend, ncol=2, nrow = 3, 
             layout_matrix = rbind(c(1,2),c(3,4), c(5,5)),
             widths = c(2.7, 2.7), heights = c(2.5, 2.5,0.2))




```

*** 

###Plotting correlations  

```{r include=FALSE}

d <- correlate(Shifting_task_individual[-1], method="pearson")
```

```{r include=FALSE}
#jpeg(file="WM_corrplot.jpeg", width=3800, height=1000, res=300)
#pdf(file="WM_corrplot.pdf", width=10, height=4)
d %>%
  shave(upper = TRUE) %>%
  rplot(print_cor = TRUE, colors = c("red", "green"), shape = 16) 
#dev.off()
#rcorr(as.matrix(WM_task_individual[-1]), type="spearman")

chart.Correlation(Shifting_task_individual[-1], histogram=TRUE, pch=19, method = "spearman")
```

```{r echo=FALSE}
# Get upper triangle of the correlation matrix
  get_upper_tri <- function(cormat){
    cormat[lower.tri(cormat)]<- NA
    return(cormat)
  }

Shifting_task_individual_corr <- Shifting_task_individual  %>% 
  select(-Shifting.tray.correct,-Shifting.tray.correct.S1,#-SD, -SR, -CD, -ID,
         -Shifting.shelf.correct, -shelf_switching_mistakes )

  
cormat <- round(cor(Shifting_task_individual_corr[-1], method="pearson", use = "pairwise.complete.obs"),2)
upper_tri <- get_upper_tri(cormat)
melted_cormat=melt(cormat, na.rm = TRUE)
ggplot(data = melted_cormat, aes(x=Var1, y=Var2, fill=value)) + 
  geom_tile()+
  geom_text(aes(Var2, Var1, label = value), color = "black", size = 2) +
 scale_fill_gradient2(low = "blue", high = "red", 
   midpoint = 0, limit = c(-1,1), space = "Lab", 
   name=" Pearson Correlation") +
  theme_minimal()+ 
 theme(axis.text.x = element_text(angle = 45, vjust = 1, 
    size = 8, hjust = 1))+
  labs(x="",y="")+
 coord_fixed()

```
```{r echo=FALSE}
knitr::knit_exit()
```

```{r include=FALSE}
library(ggcorrplot)
corr <- cor(Shifting_task_individual_corr[-1])
p.mat <- cor_pmat(Shifting_task_individual_corr[-1])
ggcorrplot(cormat, hc.order = TRUE,
    type = "lower",  lab=TRUE, insig="pch")

```

```{r include=FALSE}
write.csv(Shifting_task_individual_corr, file = "../EF_tasks/Shifting_task_individual_corr.csv", row.names = FALSE)
```


