---
title: "Lids task - Markdown"
author: "Christoph Voelter"
date: "December 13, 2018"
output:
  html_document: 
    toc: true
    toc_float: true
    toc_depth: 4
    theme: united
  #pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)


library(lme4)
library(readr)
library(tidyverse)
library(sjPlot)
library(ggthemes)
library(gridExtra)
library(reshape2)
#library(Hmisc)
library("PerformanceAnalytics")
source("C:/Users/cjv3/R/R scripts/Roger/diagnostic_fcns.r")
source("C:/Users/cjv3/R/R scripts/Roger/glmm_stability.r")
source("C:/Users/cjv3/R/R scripts/Roger/boxplotteR.r")
source("C:/Users/cjv3/R/R scripts/Roger/boot_glmm.r")
source("C:/Users/cjv3/R/R scripts/Roger/corr_exact.r")
#load(file ="mm1_mult_poss.RData")
#readRDS(file ="multpos_model.rds")
```



```{r include=FALSE}
#install.packages("exactRankTests")
library(exactRankTests)

better.wilcox=function(var1){
  test.data=data.frame(var1)
  test.data=subset( test.data, var1 !=0.5)
  N=nrow(test.data)
  w.res=wilcox.exact (test.data$var1, paired=F, exact=T, mu=0.25, alternative = c("two.sided"))
  wT=w.res$statistic
  wT=max(c(wT, N*(N+1)/2- wT))
return(data.frame(T.plus=wT, N=N, P=w.res$p.value) )
}

better.wilcox2=function(var1, var2){
  test.data=data.frame(var1, var2)
  test.data=subset( test.data, var1 != var2)
  N=nrow(test.data)
  w.res=wilcox.exact (test.data$var1, test.data$var2, paired=T, exact=T, alternative = c("two.sided"))
  wT=w.res$statistic
  wT=max(c(wT, N*(N+1)/2- wT))
return(data.frame(T.plus=wT, N=N, P=w.res$p.value) )
}
```

####Notes
* Safari excluded (he completed only 5 trials in the transparent condition within 2 sessions)  


```{r loading data, include = FALSE}
#Preparing code for mixed modeling. 
Lids.data <- read.table(file="data/20181213Lids_data_sweetwaters.txt", header=T, sep="\t") %>%
  filter(Subject != "Safari") #did not complete test trials



```

```{r eval=FALSE, include=FALSE}
summary(Lids.data )
```


##Choice performance  

### Transparent vs opaque phase

```{r lids plot, echo=FALSE}
#correct
lids_individual <- Lids.data %>%
  filter(!is.na(correct)) %>%
  group_by(Phase, Subject) %>% 
  summarize(lids.correct = mean(correct)) %>% 
  add_count(lids.correct)

  
lids_individual$Phase <- factor(lids_individual$Phase, levels = c("transparent", "opaque"))


p1<-  ggplot(
  data=lids_individual, aes(x=Phase, y=lids.correct, group=Phase)) +
  geom_boxplot()+
  geom_point(size = lids_individual$n, colour = "purple")+
  ylim(0,1)+
  #xlim(0,2)+
#  geom_line(lty=2)+
  labs(x="",y="Mean proportion of correct choices")+
  theme_few()+
  #theme(axis.text.x=element_blank(), axis.ticks.x=element_blank())+
  ggtitle("Choice performance")+
  geom_hline(yintercept=1/4, linetype="dashed", color = "red")


#peeking



lids_individual2 <- Lids.data %>%
  filter(!is.na(peeking)) %>%
  group_by(Phase, Subject) %>% 
  summarize(lids.peeking = mean(peeking)) %>% 
  add_count(lids.peeking)

  
lids_individual2$Phase <- factor(lids_individual$Phase, levels = c("transparent", "opaque"))

p2<-  ggplot(
  data=lids_individual2, aes(x=Phase, y=lids.peeking, group=Phase)) +
  geom_boxplot()+
  geom_point(size = lids_individual2$n, colour = "purple")+
  ylim(0,1)+
  #xlim(0,2)+
#  geom_line(lty=2)+
  labs(x="",y="Mean proportion of peeking")+
  theme_few()+
  #theme(axis.text.x=element_blank(), axis.ticks.x=element_blank())+
  ggtitle("Peeking")

  grid.arrange(p1, p2, nrow=1)

```


#### Comparison to chance

* DV: mean performance of correct choices.
* Chance value: 0.25

##### T-Test

```{r echo=FALSE}
tt<-t.test(lids_individual[lids_individual$Phase=="transparent",]$lids.correct, mu=1/4, alternative = "two.sided")
```
* Transparent condition (pretest): Mean = `r round(tt$estimate, 2)`, 95% CI [`r round(tt$conf.int[1],2)`, `r round(tt$conf.int[2],2)`], *t*(`r tt$parameter`)=`r round(tt$statistic,2)`, *p*=`r round(tt$p.value,5)` 

```{r echo=FALSE}
tt<-t.test( lids_individual[lids_individual$Phase=="opaque",]$lids.correct, mu=1/4, alternative = "two.sided")
```
* Opaque condition (test): Mean = `r round(tt$estimate, 2)`, 95% CI [`r round(tt$conf.int[1],2)`, `r round(tt$conf.int[2],2)`], *t*(`r tt$parameter`)=`r round(tt$statistic,2)`, *p*=`r round(tt$p.value,3)`

##### Wilcoxon

```{r echo=FALSE}
wt<-better.wilcox( lids_individual[lids_individual$Phase=="transparent",]$lids.correct) 

```
* Transparent condition (pretest):  Median = `r round(median( lids_individual[lids_individual$Phase=="transparent",]$lids.correct), 2)`, T<sup>+</sup>=`r wt$T.plus`, N=`r wt$N`, *p*=`r round(wt$P,3)`



```{r echo=FALSE}
wt<-better.wilcox( lids_individual[lids_individual$Phase=="opaque",]$lids.correct) 

```
* Opaque condition (test): Median = `r round(median( lids_individual[lids_individual$Phase=="opaque",]$lids.correct), 2)`, T<sup>+</sup>=`r wt$T.plus`, N=`r wt$N`, *p*=`r round(wt$P,3)`




### Transparent phase: trial types

```{r echo=FALSE}
#correct
lids_individual_config <- Lids.data %>%
  filter(!is.na(correct)) %>%
  filter(Phase=="transparent") %>%
  group_by(configuration, Subject) %>% 
  summarize(lids.correct = mean(correct)) %>% 
  add_count(lids.correct) 

  ggplot(
  data=lids_individual_config, aes(x=configuration, y=lids.correct, group=configuration))+
  geom_boxplot()+
  geom_point(size = lids_individual_config$n, colour = "purple")+
  ylim(0,1)+
  #xlim(0,2)+
#  geom_line(lty=2)+
  labs(x="Trial types",y="Mean number of correct choices")+
  theme_few()+
  #theme(axis.text.x=element_blank(), axis.ticks.x=element_blank())+
  ggtitle("Choice performance per trial type")+
  geom_hline(yintercept=1/4, linetype="dashed", color = "red")



```

##### T-Test

```{r echo=FALSE}
tt<-t.test(lids_individual_config[lids_individual_config$configuration=="baited",]$lids.correct, mu=1/4, alternative = "two.sided")
```
* **All baited - one open** : Mean = `r round(tt$estimate, 2)`, 95% CI [`r round(tt$conf.int[1],2)`, `r round(tt$conf.int[2],2)`], *t*(`r tt$parameter`)=`r round(tt$statistic,2)`, *p*=`r round(tt$p.value,5)` 

```{r echo=FALSE}
tt<-t.test(lids_individual_config[lids_individual_config$configuration=="mixed",]$lids.correct, mu=1/4, alternative = "two.sided")
```
* **Mixed condition** : Mean = `r round(tt$estimate, 2)`, 95% CI [`r round(tt$conf.int[1],2)`, `r round(tt$conf.int[2],2)`], *t*(`r tt$parameter`)=`r round(tt$statistic,2)`, *p*=`r round(tt$p.value,5)` 

```{r echo=FALSE}
tt<-t.test(lids_individual_config[lids_individual_config$configuration=="open",]$lids.correct, mu=1/4, alternative = "two.sided")
```
* **All open - one baited** : Mean = `r round(tt$estimate, 2)`, 95% CI [`r round(tt$conf.int[1],2)`, `r round(tt$conf.int[2],2)`], *t*(`r tt$parameter`)=`r round(tt$statistic,2)`, *p*=`r round(tt$p.value,5)`





***

### Opaque phase: trial types

```{r echo=FALSE}
#correct
lids_individual_config <- Lids.data %>%
  filter(!is.na(correct)) %>%
  filter(Phase=="opaque") %>%
  group_by(configuration, Subject) %>% 
  summarize(lids.correct = mean(correct)) %>% 
  add_count(lids.correct) 

  ggplot(
  data=lids_individual_config, aes(x=configuration, y=lids.correct, group=configuration))+
  geom_boxplot()+
  geom_point(size = lids_individual_config$n, colour = "purple")+
  ylim(0,1)+
  #xlim(0,2)+
#  geom_line(lty=2)+
  labs(x="Trial types",y="Mean number of correct choices")+
  theme_few()+
  #theme(axis.text.x=element_blank(), axis.ticks.x=element_blank())+
  ggtitle("Choice performance per trial type")+
  geom_hline(yintercept=1/4, linetype="dashed", color = "red")



```

##### T-Test

```{r echo=FALSE}
tt<-t.test(lids_individual_config[lids_individual_config$configuration=="baited",]$lids.correct, mu=1/4, alternative = "two.sided")
```
* **All baited - one open** : Mean = `r round(tt$estimate, 2)`, 95% CI [`r round(tt$conf.int[1],2)`, `r round(tt$conf.int[2],2)`], *t*(`r tt$parameter`)=`r round(tt$statistic,2)`, *p*=`r round(tt$p.value,5)` 

```{r echo=FALSE}
tt<-t.test(lids_individual_config[lids_individual_config$configuration=="mixed",]$lids.correct, mu=1/4, alternative = "two.sided")
```
* **Mixed condition** : Mean = `r round(tt$estimate, 2)`, 95% CI [`r round(tt$conf.int[1],2)`, `r round(tt$conf.int[2],2)`], *t*(`r tt$parameter`)=`r round(tt$statistic,2)`, *p*=`r round(tt$p.value,5)` 

```{r echo=FALSE}
tt<-t.test(lids_individual_config[lids_individual_config$configuration=="open",]$lids.correct, mu=1/4, alternative = "two.sided")
```
* **All open - one baited** : Mean = `r round(tt$estimate, 2)`, 95% CI [`r round(tt$conf.int[1],2)`, `r round(tt$conf.int[2],2)`], *t*(`r tt$parameter`)=`r round(tt$statistic,2)`, *p*=`r round(tt$p.value,5)`


***




##Peeking

###Comparison between transparent and opaque condition


##### T-Test

```{r echo=FALSE}
tt<-t.test(lids_individual[lids_individual$Phase=="transparent",]$lids.correct, lids_individual[lids_individual$Phase=="opaque",]$lids.correct, paired = TRUE, alternative = "two.sided")
```
* Difference between peeking response between transparent and opaque condition: Mean difference = `r round(tt$estimate, 2)`, 95% CI [`r round(tt$conf.int[1],2)`, `r round(tt$conf.int[2],2)`], *t*(`r tt$parameter`)=`r round(tt$statistic,2)`, *p*=`r round(tt$p.value,3)` 

##### Wilcoxon
```{r echo=FALSE}
wt<-better.wilcox2(lids_individual[lids_individual$Phase=="transparent",]$lids.correct, lids_individual[lids_individual$Phase=="opaque",]$lids.correct) 

```
* Difference between peeking response between transparent and opaque condition: T<sup>+</sup>=`r wt$T.plus`, N=`r wt$N`, *p*=`r wt$P`



###Peeking as function of trial types  


```{r  echo=FALSE}

##peeking overall
lids_individual3 <- Lids.data %>%
  filter(!is.na(peeking)) %>%
  filter(Phase=="opaque") %>%
  group_by(configuration, Subject) %>% 
  summarize(lids.peeking = mean(peeking)) %>% 
  add_count(lids.peeking)

  
lids_mean3<-lids_individual3%>%
  group_by(configuration) %>% 
  summarize(lids.peeking = mean(lids.peeking))

#p1<-  
ggplot(
  data=lids_individual3, aes(x=configuration, y=lids.peeking, group=configuration)) +
  #geom_boxplot()+
  geom_bar(data = lids_mean3, stat = "identity", alpha = .3)+
  geom_point(size = lids_individual3$n, colour = "purple")+
  ylim(0,1)+
  #xlim(0,2)+
#  geom_line(lty=2)+
  labs(x="Visible configuration",y="Mean proportion of peeking")+
  theme_few()+
  #theme(axis.text.x=element_blank(), axis.ticks.x=element_blank())+
  ggtitle("Peeking - opaque condition")
```

```{r echo=FALSE}
lids_individual4 <- Lids.data %>%
  filter(!is.na(peek_above)) %>%
  filter(Phase=="opaque") %>%
  group_by(configuration, Subject) %>% 
  summarize(lids.peek_above = mean(peek_above)) %>% 
  add_count(lids.peek_above)

lids_mean4<-lids_individual4%>%
  group_by(configuration) %>% 
  summarize(lids.peek_above = mean(lids.peek_above))

#p2<-  
ggplot(
  data=lids_individual4, aes(x=configuration, y=lids.peek_above, group=configuration)) +
  #geom_boxplot()+
  geom_bar(data = lids_mean4, stat = "identity", alpha = .3)+
  geom_point(size = lids_individual4$n, colour = "purple")+
  ylim(0,1)+
  #xlim(0,2)+
#  geom_line(lty=2)+
  labs(x="Visible configuration",y="Mean proportion of peeking above")+
  theme_few()+
  #theme(axis.text.x=element_blank(), axis.ticks.x=element_blank())+
  ggtitle("Peeking above - opaque condition")

```

```{r echo=FALSE}
##Peeking below
lids_individual5 <- Lids.data %>%
  filter(!is.na(peek_below)) %>%
  filter(Phase=="opaque") %>%
  group_by(configuration, Subject) %>% 
  summarize(lids.peek_below = mean(peek_below)) %>% 
  add_count(lids.peek_below)


lids_mean5<-lids_individual5%>%
  group_by(configuration) %>% 
  summarize(lids.peek_below = mean(lids.peek_below))

#p3<-  
ggplot(
  data=lids_individual5, aes(x=configuration, y=lids.peek_below, group=configuration)) +
#  geom_boxplot()+
  geom_bar(data = lids_mean5, stat = "identity", alpha = .3)+
  geom_point(size = lids_individual5$n, colour = "purple")+
  ylim(0,1)+
  #xlim(0,2)+
#  geom_line(lty=2)+
  labs(x="Visible configuration",y="Mean proportion of peeking below")+
  theme_few()+
  #theme(axis.text.x=element_blank(), axis.ticks.x=element_blank())+
  ggtitle("Peeking below - opaque condition")


 #grid.arrange(p1, p2,p3)

```


***  

## Relationship between peeking and choice performance

###Opaque phase: peeking vs no peeking

```{r lids plot3, echo=FALSE}
#correct
lids_individual_peek <- Lids.data %>%
  filter(!is.na(correct)) %>%
  filter(Phase=="opaque") %>%
  group_by(peeking, Subject) %>% 
  summarize(lids.correct = mean(correct)) %>% 
  add_count(lids.correct) %>%
  ungroup() %>% 
  mutate(peeking=recode(peeking, `0`="No", `1`="Yes"))

  ggplot(
  data=lids_individual_peek, aes(x=peeking, y=lids.correct, group=peeking)) +
  geom_boxplot()+
  geom_point(size = lids_individual_peek$n, colour = "purple")+
  ylim(0,1)+
  #xlim(0,2)+
#  geom_line(lty=2)+
  labs(x="Peeking",y="Mean number of correct choices")+
  theme_few()+
  #theme(axis.text.x=element_blank(), axis.ticks.x=element_blank())+
  ggtitle("Choice performance")+
  geom_hline(yintercept=1/4, linetype="dashed", color = "red")



```

##### T-Test

```{r echo=FALSE}
tt<-t.test( lids_individual_peek[lids_individual_peek $peeking=="No",]$lids.correct, mu=1/4, alternative = "two.sided")
```
* Opaque condition - **No peeking**: Mean = `r round(tt$estimate, 2)`, 95% CI [`r round(tt$conf.int[1],2)`, `r round(tt$conf.int[2],2)`], *t*(`r tt$parameter`)=`r round(tt$statistic,2)`, *p*=`r round(tt$p.value,3)`


```{r echo=FALSE}
tt<-t.test( lids_individual_peek[lids_individual_peek $peeking=="Yes",]$lids.correct, mu=1/4, alternative = "two.sided")
```
* Opaque condition - **Peeking**: Mean = `r round(tt$estimate, 2)`, 95% CI [`r round(tt$conf.int[1],2)`, `r round(tt$conf.int[2],2)`], *t*(`r tt$parameter`)=`r round(tt$statistic,2)`, *p*=`r round(tt$p.value,3)`

##### Wilcoxon
```{r echo=FALSE}
wt<-better.wilcox(lids_individual_peek[lids_individual_peek $peeking=="No",]$lids.correct) 

```
* Opaque condition - **No Peeking**: Median = `r round(median(lids_individual_peek[lids_individual_peek $peeking=="No",]$lids.correct), 2)`, T<sup>+</sup>=`r wt$T.plus`, N=`r wt$N`, *p*=`r round(wt$P,3)`

```{r echo=FALSE}
wt<-better.wilcox(lids_individual_peek[lids_individual_peek $peeking=="Yes",]$lids.correct) 

```
* Opaque condition - **Peeking**: Median = `r round(median(lids_individual_peek[lids_individual_peek $peeking=="Yes",]$lids.correct), 2)`, T<sup>+</sup>=`r wt$T.plus`, N=`r wt$N`, *p*=`r round(wt$P,3)`


#### Only individuals who peek (at least once)

```{r lids plot4, echo=FALSE}
#correct
lids_individual_peek2 <- Lids.data %>%
  group_by(Subject) %>% 
  summarize(lids.peeking = mean(peeking))

filt<-as.vector(lids_individual_peek2[lids_individual_peek2$lids.peeking==0,]$Subject)

lids_individual_peek3 <- lids_individual_peek %>%
  filter(!(Subject %in% filt)) %>%#removing subjects that did not peek at all
  select(-n)%>%
  add_count(lids.correct)


  ggplot(
  data=lids_individual_peek3, aes(x=peeking, y=lids.correct, group=peeking)) +
  geom_boxplot()+
  geom_point(size = lids_individual_peek3$n, colour = "purple")+
  ylim(0,1)+
  #xlim(0,2)+
#  geom_line(lty=2)+
  labs(x="Peeking",y="Mean number of correct choices")+
  theme_few()+
  #theme(axis.text.x=element_blank(), axis.ticks.x=element_blank())+
  ggtitle("Choice performance")+
  geom_hline(yintercept=1/4, linetype="dashed", color = "red")



```

##### T-Test  

```{r echo=FALSE}
tt<-t.test( lids_individual_peek3[lids_individual_peek3 $peeking=="No",]$lids.correct, mu=1/4, alternative = "two.sided")
```
* Opaque condition - **No peeking**: Mean = `r round(tt$estimate, 2)`, 95% CI [`r round(tt$conf.int[1],2)`, `r round(tt$conf.int[2],2)`], *t*(`r tt$parameter`)=`r round(tt$statistic,2)`, *p*=`r round(tt$p.value,3)`


```{r echo=FALSE}
tt<-t.test( lids_individual_peek3[lids_individual_peek3 $peeking=="Yes",]$lids.correct, mu=1/4, alternative = "two.sided")
```
* Opaque condition - **Peeking**: Mean = `r round(tt$estimate, 2)`, 95% CI [`r round(tt$conf.int[1],2)`, `r round(tt$conf.int[2],2)`], *t*(`r tt$parameter`)=`r round(tt$statistic,2)`, *p*=`r round(tt$p.value,3)`


##### Wilcoxon


```{r echo=FALSE}
wt<-better.wilcox(lids_individual_peek3[lids_individual_peek3 $peeking=="No",]$lids.correct) 

```
* Opaque condition - **No Peeking**: Median = `r round(median(lids_individual_peek3[lids_individual_peek3 $peeking=="No",]$lids.correct), 2)`, T<sup>+</sup>=`r wt$T.plus`, N=`r wt$N`, *p*=`r round(wt$P,3)`

```{r echo=FALSE}
wt<-better.wilcox(lids_individual_peek3[lids_individual_peek3 $peeking=="Yes",]$lids.correct) 

```
* Opaque condition - **Peeking**: Median = `r round(median(lids_individual_peek3[lids_individual_peek3 $peeking=="Yes",]$lids.correct), 2)`, T<sup>+</sup>=`r wt$T.plus`, N=`r wt$N`, *p*=`r round(wt$P,3)`



***  


```{r echo=FALSE}
knitr::knit_exit()
```


####GLMM 01

look ~ Test phase + Trial number within phase + Age + (1+Test phase + Trial number within phase | Subject), family = binomial.

+ Scale variables: trial number, age, and order of conditions
```{R include=FALSE}
Lids.data$z.trial=as.vector(scale(Lids.data$trial_number))
Lids.data$z.age=as.vector(scale(Lids.data$Age))
```


```{r}
#coding dummy variables before centering the slopes
Lids.data$Condition.c<-as.numeric(Lids.data$Phase==levels(Lids.data$Phase)[2])
Lids.data$Condition.c=Lids.data$Condition.c-mean(Lids.data$Condition.c)

```

### Run Model

####Full model
```{r}
contr=glmerControl(optimizer="bobyqa", optCtrl=list(maxfun=10000000))
glmm01=glmer(peeking ~ Phase+z.trial+z.age+
               (1+z.trial+Phase|Subject),
             data=Lids.data, family=binomial, control=contr)
```


####Null model	 
```{r}	 
null01=glmer(peeking ~ 1+(1+z.trial+Phase|Subject),
             data=Lids.data, family=binomial, control=contr)
```
####Full-null model comparison
```{r echo=FALSE}	 
round(anova(null01, glmm01, test="Chisq"),3)
```

```{r}
xdrop1=drop1(glmm01, test="Chisq",control=contr)
round(xdrop1,3)
```




####GLMM 02a
GLMM2a: To analyse the effects of condition (within the test phase only) on participants looking above the occluder / double-cylinders:
Presence of above looks ~ Condition + Trial number within test phase + Age + (1+Condition + Trial number within test phase | Subject), family =binomial

```{r}

Lids.data.opaque<-Lids.data%>%
  filter(Phase=="opaque")
```


+ Scale variables: trial number, age, and order of conditions
```{R include=FALSE}
Lids.data.opaque$z.trial=as.vector(scale(Lids.data.opaque$trial_number))
Lids.data.opaque$z.age=as.vector(scale(Lids.data.opaque$Age))
```


```{r}
#coding dummy variables before centering the slopes
Lids.data.opaque$Condition.c<-as.numeric(Lids.data.opaque$Phase==levels(Lids.data.opaque$Phase)[2])
Lids.data.opaque$Condition.c=Lids.data.opaque$Condition.c-mean(Lids.data.opaque$Condition.c)

```

### Run Model

####Full model
```{r}
contr=glmerControl(optimizer="bobyqa", optCtrl=list(maxfun=10000000))
glmm02a=glmer(peek_above ~ configuration+z.trial+z.age+
              (1|Subject)+(0+z.trial+configuration|Subject),
             data=Lids.data.opaque, family=binomial, control=contr)
```


####Null model	 
```{r}	 
null02a=glmer(peek_above ~ 1+
               (1|Subject)+(0+z.trial+configuration|Subject),
             data=Lids.data.opaque, family=binomial, control=contr)
```
####Full-null model comparison
```{r echo=FALSE}	 
round(anova(null02a, glmm02a, test="Chisq"),3)
```

```{r}
xdrop2a=drop1(glmm02a, test="Chisq",control=contr)
round(xdrop2c,3)
```





####GLMM 02c
GLMM2c: To analyse the effects of condition (within the test phase only) on participants looking both above and below the occluder / double-cylinders:
Presence of both an above and a below look ~ Condition + Trial number within test phase  + Age + (1+Condition + Trial number within test phase | Subject), family =binomial

```{r}

Lids.data.opaque<-Lids.data%>%
  filter(Phase=="opaque")
```


+ Scale variables: trial number, age, and order of conditions
```{R include=FALSE}
Lids.data.opaque$z.trial=as.vector(scale(Lids.data.opaque$trial_number))
Lids.data.opaque$z.age=as.vector(scale(Lids.data.opaque$Age))
```


```{r}
#coding dummy variables before centering the slopes
Lids.data.opaque$Condition.c<-as.numeric(Lids.data.opaque$Phase==levels(Lids.data.opaque$Phase)[2])
Lids.data.opaque$Condition.c=Lids.data.opaque$Condition.c-mean(Lids.data.opaque$Condition.c)

```

### Run Model

####Full model
```{r}
contr=glmerControl(optimizer="bobyqa", optCtrl=list(maxfun=10000000))
glmm02c=glmer(peeking ~ configuration+z.trial+z.age+
              (1|Subject)+(0+z.trial+configuration|Subject),
             data=Lids.data.opaque, family=binomial, control=contr)
```


####Null model	 
```{r}	 
null02c=glmer(peeking ~ 1+
               (1|Subject)+(0+z.trial+configuration|Subject),
             data=Lids.data.opaque, family=binomial, control=contr)
```
####Full-null model comparison
```{r echo=FALSE}	 
round(anova(null02c, glmm02c, test="Chisq"),3)
```

```{r}
xdrop2c=drop1(glmm02c, test="Chisq",control=contr)
round(xdrop2c,3)
```




```{r echo=FALSE}
knitr::knit_exit()
```

